Exploring Feature Engineering

### 2019-03-22 Scripts/evaluating_correlations.Rmd
saving gm12878 and k562 corr plots

corfunction <- function(resolution, predictortype, annotation){

@@

@@

>>>>

corfunction <- function(cl, resolution, predictortype, annotation){
  #set up variable names to subset
  chromstatevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/BroadHMM"))
  histonevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/HistoneModifications"))
  if(cl=="GM12878"){
    tfbsvars <-  gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/gm12878"))
  } else {
    tfbsvars <-  gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/k562"))
  }

  if(cl=="GM12878"){
    datadir = paste("Z:/TAD_data_analysis/", cl, "/", resolution, "/Ensemble/PCA", 
                    "/pcadat_gm12878_", resolution, "_", predictortype, ".rds",
                    sep="")
  }else{datadir = paste("Z:/TAD_data_analysis/", cl, "/", resolution, "/Ensemble/PCA", 
                    "/pcadat_", cl, "_", resolution, "_", predictortype, ".rds",
                    sep="")}

  data <- readRDS(datadir)
  colnames(data) <- gsub(paste("_", predictortype, sep=""),"",colnames(data))

  if(annotation=="chromstates"){
    data <- data[,which(colnames(data) %in% chromstatevars)];
    colnames(data) <- gsub(paste(c("Gm12878", "K562",
                          "-",
                          "_",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(data))
  } else if(annotation=="histones"){
    data <- data[,which(colnames(data) %in% histonevars)];
    colnames(data) <- gsub(paste(c("Gm12878", "K562",
                          "-",
                          "_",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(data))
  } else if(annotation=="tfbs"){
    data <- data[,which(colnames(data) %in% tfbsvars)];
    colnames(data) <- gsub(paste(c("Gm12878", "K562",
                          "-",
                          "_",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(data))
  }

  if(predictortype=="count" | predictortype=="perc"){
    cormat <- cor(data, method = "spearman")
  } else {
    cormat <- cor(data, method = "pearson")
  }

  png(filename = paste("C:/Users/stili/Documents/TAD_miscellaneous/figures/correlation_plots/", 
                       cl, resolution, predictortype, annotation,
                       ".png", sep=""),
      width=11, height=8, units="in", res = 300)
  corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         tl.cex = .5,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))
  dev.off()

@@

corfunction(cl = "GM12878", resolution = "10kb", predictortype = "count", annotation = "chromstates")
corfunction(cl = "GM12878", resolution = "10kb", predictortype = "count", annotation = "histones")
corfunction(cl = "GM12878", resolution = "10kb", predictortype = "count", annotation = "tfbs")

corfunction(cl = "GM12878", resolution = "10kb", predictortype = "perc", annotation = "chromstates")
corfunction(cl = "GM12878", resolution = "10kb", predictortype = "perc", annotation = "histones")
corfunction(cl = "GM12878", resolution = "10kb", predictortype = "perc", annotation = "tfbs")

corfunction(cl = "GM12878", resolution = "10kb", predictortype = "dist", annotation = "chromstates")
corfunction(cl = "GM12878", resolution = "10kb", predictortype = "dist", annotation = "histones")
corfunction(cl = "GM12878", resolution = "10kb", predictortype = "dist", annotation = "tfbs")

corfunction(cl = "GM12878", resolution = "25kb", predictortype = "count", annotation = "chromstates")
corfunction(cl = "GM12878", resolution = "25kb", predictortype = "count", annotation = "histones")
corfunction(cl = "GM12878", resolution = "25kb", predictortype = "count", annotation = "tfbs")

corfunction(cl = "GM12878", resolution = "25kb", predictortype = "perc", annotation = "chromstates")
corfunction(cl = "GM12878", resolution = "25kb", predictortype = "perc", annotation = "histones")
corfunction(cl = "GM12878", resolution = "25kb", predictortype = "perc", annotation = "tfbs")

corfunction(cl = "GM12878", resolution = "25kb", predictortype = "dist", annotation = "chromstates")
corfunction(cl = "GM12878", resolution = "25kb", predictortype = "dist", annotation = "histones")
corfunction(cl = "GM12878", resolution = "25kb", predictortype = "dist", annotation = "tfbs")

corfunction(cl = "GM12878", resolution = "50kb", predictortype = "count", annotation = "chromstates")
corfunction(cl = "GM12878", resolution = "50kb", predictortype = "count", annotation = "histones")
corfunction(cl = "GM12878", resolution = "50kb", predictortype = "count", annotation = "tfbs")

corfunction(cl = "GM12878", resolution = "50kb", predictortype = "perc", annotation = "chromstates")
corfunction(cl = "GM12878", resolution = "50kb", predictortype = "perc", annotation = "histones")
corfunction(cl = "GM12878", resolution = "50kb", predictortype = "perc", annotation = "tfbs")

corfunction(cl = "GM12878", resolution = "50kb", predictortype = "dist", annotation = "chromstates")
corfunction(cl = "GM12878", resolution = "50kb", predictortype = "dist", annotation = "histones")
corfunction(cl = "GM12878", resolution = "50kb", predictortype = "dist", annotation = "tfbs")

corfunction(cl = "GM12878", resolution = "100kb", predictortype = "count", annotation = "chromstates")
corfunction(cl = "GM12878", resolution = "100kb", predictortype = "count", annotation = "histones")
corfunction(cl = "GM12878", resolution = "100kb", predictortype = "count", annotation = "tfbs")

corfunction(cl = "GM12878", resolution = "100kb", predictortype = "perc", annotation = "chromstates")
corfunction(cl = "GM12878", resolution = "100kb", predictortype = "perc", annotation = "histones")
corfunction(cl = "GM12878", resolution = "100kb", predictortype = "perc", annotation = "tfbs")

corfunction(cl = "GM12878", resolution = "100kb", predictortype = "dist", annotation = "chromstates")
corfunction(cl = "GM12878", resolution = "100kb", predictortype = "dist", annotation = "histones")
corfunction(cl = "GM12878", resolution = "100kb", predictortype = "dist", annotation = "tfbs")

@@

#### Saving K562 Correlation Plots

```{r}
corfunction(cl = "K562", resolution = "25kb", predictortype = "count", annotation = "chromstates")
corfunction(cl = "K562", resolution = "25kb", predictortype = "count", annotation = "histones")
corfunction(cl = "K562", resolution = "25kb", predictortype = "count", annotation = "tfbs")

corfunction(cl = "K562", resolution = "25kb", predictortype = "perc", annotation = "chromstates")
corfunction(cl = "K562", resolution = "25kb", predictortype = "perc", annotation = "histones")
corfunction(cl = "K562", resolution = "25kb", predictortype = "perc", annotation = "tfbs")

corfunction(cl = "K562", resolution = "25kb", predictortype = "dist", annotation = "chromstates")
corfunction(cl = "K562", resolution = "25kb", predictortype = "dist", annotation = "histones")
corfunction(cl = "K562", resolution = "25kb", predictortype = "dist", annotation = "tfbs")

corfunction(cl = "K562", resolution = "50kb", predictortype = "count", annotation = "chromstates")
corfunction(cl = "K562", resolution = "50kb", predictortype = "count", annotation = "histones")
corfunction(cl = "K562", resolution = "50kb", predictortype = "count", annotation = "tfbs")

corfunction(cl = "K562", resolution = "50kb", predictortype = "perc", annotation = "chromstates")
corfunction(cl = "K562", resolution = "50kb", predictortype = "perc", annotation = "histones")
corfunction(cl = "K562", resolution = "50kb", predictortype = "perc", annotation = "tfbs")

corfunction(cl = "K562", resolution = "50kb", predictortype = "dist", annotation = "chromstates")
corfunction(cl = "K562", resolution = "50kb", predictortype = "dist", annotation = "histones")
corfunction(cl = "K562", resolution = "50kb", predictortype = "dist", annotation = "tfbs")

corfunction(cl = "K562", resolution = "100kb", predictortype = "count", annotation = "chromstates")
corfunction(cl = "K562", resolution = "100kb", predictortype = "count", annotation = "histones")
corfunction(cl = "K562", resolution = "100kb", predictortype = "count", annotation = "tfbs")

corfunction(cl = "K562", resolution = "100kb", predictortype = "perc", annotation = "chromstates")
corfunction(cl = "K562", resolution = "100kb", predictortype = "perc", annotation = "histones")
corfunction(cl = "K562", resolution = "100kb", predictortype = "perc", annotation = "tfbs")

corfunction(cl = "K562", resolution = "100kb", predictortype = "dist", annotation = "chromstates")
corfunction(cl = "K562", resolution = "100kb", predictortype = "dist", annotation = "histones")
corfunction(cl = "K562", resolution = "100kb", predictortype = "dist", annotation = "tfbs")
